Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-06 paper-v1.tex
few changes mostly on the style

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent blockchain engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
blockchain for science here and application to open science and to peer review as a specific case
An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

\section{Background}
\subsection{Peer-review: problem}
Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times. Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications. This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research. Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work. On top of this, author-level metrics that measure the scientific impact and productivity of academics, such as the h-index, and are taken into account by the funding agencies, are purely based on the number of citations per each publications while neglecting the full spectrum of scientific contributions (software, data collection, presentations, reviews…). Therefore, peer-reviewing is an intellectual investment without any external return for researchers’ career. A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5]. Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas). Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...). These trust problems are one of the major issues facing scholarly communication.

\subsubsection{Types of peer-review}
\begin{itemize}
    \item single-blind peer review
    \item double-blind peer review
    \item transparent peer review
\end{itemize}

\subsubsection{Traditional peer-review process}
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves. 
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. 
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

\subsection{Related work}

Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.

Crossref primary DOI provider, announced that review reports could be now registered as part of their services
Publons provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
ScienceOpen
DEIP
Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
Peerage of Science that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews. 
Blockchain for Peer Review, pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []

The project will develop a protocol where information about peer review activities (submitted by publishers) are stored on a blockchain. This will allow the review process to be independently validated, and data to be fed to relevant vehicles to ensure recognition and validation for reviewers.  By sharing peer review information, while adhering to laws on privacy, data protection and confidentiality, we will foster innovation and increase interoperability.

\section{System concept}
For the above mentioned reasons, we propose an incentive-based protocol called Ants-Review to reward open peer-reviews while preserving the anonymity of the reviewers. The name originates from the idea that the work behind a finished scientific paper resembles a complex organism such as an anthill, which emerges from the sum of many individualities: in it, all contributions (even if ‘micro’) are essential to the whole and are worth recognition.
This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
Anonymity
Accountability
Reputation
Reward
Gamification model

open identities open reports open participation open interaction open platform ('decoupled review')

@@

\subsubsection{AnstReview process: scenario 2  (community-driven):

peer-review is decoupled from journal
or to the pre-print service or to an hypothetical AntsReview platform).
\subsection{Implementation}
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

@@

\subsubsection{Quadratic Funding}

\subsubsection{Privacy}

>>>>

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent blockchain engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
blockchain for science here and application to open science and to peer review as a specific case

An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: 
\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; 
\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
\paragraph{Transparency} (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

\section{Background}
\subsection{Peer-review: a flawed and outdated system}
Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times. 
\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications. 
\paragraph{Traditional peer-review process}
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves. 
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. 
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

\end{enumerate}
\subsubsection{It's unaccredited and unpaid.} This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research. Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work. On top of this, author-level metrics that measure the scientific impact and productivity of academics, such as the h-index, and are taken into account by the funding agencies, are purely based on the number of citations per each publications while neglecting the full spectrum of scientific contributions (software, data collection, presentations, reviews…). Therefore, peer-reviewing is an intellectual investment without any external return for researchers’ career. A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5]. 
\subsubsection{It's vulnerable to bias and fraud.} Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas). Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...). These trust problems are one of the major issues facing scholarly communication.

\subsubsection{Types of peer-review}
\begin{itemize}
    \item single-blind peer review
    \item double-blind peer review
    \item transparent peer review
    open identities open reports open participation open interaction open platform ('decoupled review')
\end{itemize}

\subsection{Related work}
Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index. 
In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
ScienceOpen
\emph{DEIP}
Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews. 
\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
\emph{ReviewCoin}
\emph{I8X Platform}

\subsection{Blockchain solution}

\section{System concept}
For the above mentioned reasons, we propose an incentive-based protocol called Ants-Review to reward open peer-reviews while preserving the anonymity of the reviewers. The name originates from the idea that the work behind a finished scientific paper resembles a complex organism such as an anthill, which emerges from the sum of many individualities: in it, all contributions (even if ‘micro’) are essential to the whole and are worth recognition.
This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
\paragraph{Anonymity} zSNARK
\paragraph{Accountability} hash
\paragraph{Reward} bounty

@@

\subsubsection{AnstReview process: scenario 2  (community-driven)}:

\begin{enumerate}
    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform).
    \item The paper is accepted by the community for revision in its whatever format.
    \item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
    \item (footnote?) the bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community/contributors.
    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
    \item Not all reviews will have the same quality and depth. However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript. In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community with Quadratic Voting.
    \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty. Since it's in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit. It will also fuel ethical behaviour.

peer-review is decoupled from journal
or

\subsection{Implementation}
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

@@

\subsubsection{Quadratic Voting} I don't see the point of introducing QF here. Is it already implemented or it's just in the idea?

\subsubsection{Privacy}. AZTEC protocol is a cryptographic protocol combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
